Response to the defense feedback

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

While removing secret-dependent memory-access patterns in existing software completely is hard and tedious, fixing some of the most dangerous leakages appears to be feasible. Previous studies~\cite{182946,203878,182946,236338,217537,langley2010ctgrind,xiao2017stacco,wang2019time,Wichelmann:2018:MFF:3274694.3274741,bao2021abacus} on side-channel detections have shown their effectiveness in finding such code patterns. Developers can run the tool to analyze the side-channels leakages and fix these patterns. However, fixing all these leakages seem impossible for the following reasons. First, side-channels are inevitable. For example, tremendous efforts have been made to remove the side-channel vulnerabilities in cryptography libraries in the past decade. However, we still find that there are plenty of side-channel leakages in the latest version of OpenSSL. Second, many side-channel vulnerable versions usually have better performance, such as the T-table lookups in AES, CRT optimizations in RSA, and Fast Discrete Fourier Transform (FDFT) in many media processing libraries. Third, some developers are not interested in fixing side-channels vulnerabilities unless people can show them an attack demo, even for the cryptography developers. For many non-cryptography developers, side-channels are not in the threat model. However, recent studies have shown a series of attacks on the non-cryptography libraries.

>>>>

While removing secret-dependent memory-access patterns in existing software completely is hard and tedious, fixing some of the most dangerous leakages appears to be feasible. Previous studies~\cite{182946,203878,182946,236338,217537,langley2010ctgrind,xiao2017stacco,wang2019time,Wichelmann:2018:MFF:3274694.3274741,bao2021abacus} on side-channel detections have shown their effectiveness in finding such code patterns. Developers can run the tool to analyze the side-channels leakages and fix these patterns. However, fixing all
those leakages seem not feasible in practice.  Tremendous efforts havebeen made to remove the side-channel vulnerabilities in cryptography
libraries in the past decade. However,  there are
several side-channel leakages in the recent versions of OpenSSL~\cite{OpenSSL-1.1.1-note}. Besides, many side-channel vulnerable versions usually
have better performance, such as the T-table lookups in AES, CRT
optimizations in RSA, and Fast Fourier Transform (FFT) in many media
processing libraries. For many non-cryptography developers, side
channels are not in consideration usually. However, recent
studies~\cite{xu2015controlled,191010,hahnel2017high} have shown a series of attacks on the non-cryptography libraries.
